---
title: "Country Music Topic Sources"
date: 2020-03-13T14:19:53-05:00
draft: false
links:
  - icon_pack: fab
    name: Docs
    url: courses/example1
  - icon_pack: fab
    name: Slides
    url: slides/example
  - icon_pack: fab
    name: Project
    url: project1/internal-project
bibliography: /home/redapemusic35/VimWiki/Exported-Items.bib
---

### The Thought Experiment

One of the books that I have been working my way through, is a collection of papers on the phenomenon of empathy [@copl11b]. The collection of papers all seek to articulate the phenomenon of empathy as a means of "mind reading," meaning that empathy helps us to understand or to predict what another might do. Empathy may also help to explain what emotions that person is experiencing, etc. @stum10 has a similar treatment of mind reading according to which she argues that narratives provide a way to have what she calls "second personal knowledge." Accordingly, there are two ways in which I might be acquainted with another; the first is that I might know certain facts about that person. That they like strawberry flavored ice cream, ride a bike to class 3 days a week, and have never been outside of the country. However, there is another way in which I can come to know a person, and this is through acquaintance. Further, it seems as though this kind of knowledge can only be had through acquaintance, and that narratives can provide a vehicle by which this acquaintance happens. As such, narratives help us to know others second personally.

Why is all of this important? Well, in @copl11b's book, No&euml;l @carr10 writes about the emotive responses of audiences to fictional characters in narratives. He outlines a number of ways in which the emotions of the audiences either converge, are congruent with, or resonate with those of the characters.

Some relationships between characters and their audiences which he examines:

1. Coincidentally occurring emotions:
   1. the antipathy element of solidarity
   2. Vectrially converging emotions---these can encompass certain episodes of sympathetic feeling
2. Mirror reflexes---affective states---these are not fully articulated emotions, but can contribute to their formation.


If Stump is right, or if I am right in representing her argument, one way in which we can know someone, is by having the same, or similar feelings as the person in response to the same object. One particularly interesting aspect of this discussion is Carroll's idea that sympathy for a character governs whether the audience will empathize with that character [@carr10, 174]. Further, what determines whether the audience will sympathize with a character, is whether the audience is capable of having altruistic attitudes towards the characters in question. In order to experience emotions of altruism, the audience perceives them as morally good. However, sometimes what causes us to determine whether someone is morally good, is that their interests align with ours, or whether that person's interests align with those of her community in a way in which our own would in a similar situation. Carroll calls these kinds of factors factors of kinship, group membership, group interests etc. We like people who get along well, and care about those in their community who are good, and we resonate and therefore sympathize with them.

In one of my earlier posts, I stated that it seems that country music uses more relationship words than hip-hop, and that positive emotional sentiments are often expressed in the presence of relationships whereas negative emotional sentiments are expressed when those relationships become threatened. 

Conversely, it seems that the opposite is true in many contemporary and popular hip-hop songs. Positive emotional sentiments are expressed in context of objects rather than people whereas negative emotional sentiments are expressed in terms of human relationships. Therefore, if we are to say that morality is about relationships between people, then one way to possibly measure moral knowledge in a narrative, would be to determine whether the narrative is about relationships, and whether it expresses what we might think ought to be expressed in the same or similar context. 

First, to understand how important relationships among people may be in country music, I will run some topic analyses on billboard's country top 50 for May 23, 2020.

##### Country Music Files

```{r List Files}

data <- read.delim("/home/redapemusic35/VimWiki/subjects/projects/tutorial/countrycharts.txt")

summary(data)

```

Next, I will import the lyrics to these songs:

```{r}

files <- list.files(path = "/home/redapemusic35/VimWiki/subjects/projects/lyrics/country-txt-files/", pattern = NULL, all.files = FALSE, full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE)

files

```


```{r}

lyrics <- read.csv("/home/redapemusic35/VimWiki/subjects/projects/lyrics/country-lyrics.csv", header = TRUE, stringsAsFactors = FALSE)

str(lyrics)
head(lyrics$FileName)
tail(lyrics$FileName)
head(lyrics$Content)
tail(lyrics$Content)
```

```{r}
library(magrittr)
library(ggplot2)
library(gridExtra)
library(tidytext)
library(wordcloud2)
library(dplyr)
library(readr)

names(lyrics)

glimpse(lyrics[30,])

dim(lyrics)

str(lyrics[10, ]$Content, nchar.max = 300)

fix.contractions <- function(doc) {
  doc <- gsub("won't", "will not", doc)
  doc <- gsub("can't", "can not", doc)
  doc <- gsub("n't", " not", doc)
  doc <- gsub("'re", " are", doc)
  doc <- gsub("'ve", " have", doc)
  doc <- gsub("'m", " am", doc)
  doc <- gsub("'d", " would", doc)
  doc <- gsub("flyin'", "flying", doc)
  doc <- gsub("'s", "", doc)
  doc <- gsub("Puttin'", "Putting", doc)
  doc <- gsub("I'll", "I will", doc)
  doc <- gsub("payin'", "paying", doc)
  doc <- gsub("we'll", "we will", doc)
  doc <- gsub("We'll", "We will", doc)
  doc <- gsub("singin'", "singing", doc)
  doc <- gsub("you'll", "you will", doc)
  doc <- gsub("'em", "them", doc)
  doc <- gsub("dancin'", "dancing", doc)
  doc <- gsub("playin'", "playing", doc)
  doc <- gsub("ain't", "have not", doc)
  doc <- gsub("Ain't", "Have not", doc)
  doc <- gsub("They'll", "They will", doc)
  doc <- gsub("they'll", "they will", doc)
  doc <- gsub("gettin'", "getting", doc)
  doc <- gsub("ain't", "am not", doc)
  doc <- gsub("Gettin'", "getting", doc)
  doc <- gsub("'cause", "be cause", doc)
  doc <- gsub("'Cause", "Because", doc)
  doc <- gsub("Ballin'", "Balling", doc)
  doc <- gsub("ballin'", "balling", doc)
  doc <- gsub("'cause", "because", doc)
  return(doc)
}

lyrics$Content <- sapply(lyrics$Content, fix.contractions)

# function to remove special characters

removeSpecialChars <- function(x) gsub("[^a-zA-Z0-9 ]", " ", x)

# remove special characters

# Show how many observations and columns there are
dim(lyrics)

# Other details of the created data file.
str(lyrics)

# function to remove special characters

# remove special characters

# convert everything to lower case
lyrics$Content <- sapply(lyrics$Content, tolower)

str(lyrics[9, ]$Content, nchar.max = 300)


lyrics$Content
summary(lyrics)


```

## Topic Analysis on Country's Top Songs

```{r}
library(magrittr)
library(ggplot2)
library(gridExtra)
library(tidytext)
library(wordcloud2)
library(dplyr)
library(readr)

setwd("/home/redapemusic35/VimWiki/subjects/projects/lyrics/")
lyrics <- read.csv("country-lyrics.csv", header = TRUE, stringsAsFactors = FALSE)

fix.contractions <- function(doc) {
  doc <- gsub("won't", "will not", doc)
  doc <- gsub("can't", "can not", doc)
  doc <- gsub("n't", " not", doc)
  doc <- gsub("'re", " are", doc)
  doc <- gsub("'ve", " have", doc)
  doc <- gsub("'m", " am", doc)
  doc <- gsub("'d", " would", doc)
  doc <- gsub("flyin'", "flying", doc)
  doc <- gsub("'s", "", doc)
  doc <- gsub("Puttin'", "Putting", doc)
  doc <- gsub("I'll", "I will", doc)
  doc <- gsub("payin'", "paying", doc)
  doc <- gsub("we'll", "we will", doc)
  doc <- gsub("We'll", "We will", doc)
  doc <- gsub("singin'", "singing", doc)
  doc <- gsub("you'll", "you will", doc)
  doc <- gsub("'em", "them", doc)
  doc <- gsub("dancin'", "dancing", doc)
  doc <- gsub("playin'", "playing", doc)
  doc <- gsub("ain't", "have not", doc)
  doc <- gsub("Ain't", "Have not", doc)
  doc <- gsub("They'll", "They will", doc)
  doc <- gsub("they'll", "they will", doc)
  doc <- gsub("gettin'", "getting", doc)
  doc <- gsub("ain't", "am not", doc)
  doc <- gsub("Gettin'", "getting", doc)
  doc <- gsub("'cause", "be cause", doc)
  doc <- gsub("'Cause", "Because", doc)
  doc <- gsub("Ballin'", "Balling", doc)
  doc <- gsub("ballin'", "balling", doc)
  doc <- gsub("'cause", "because", doc)
  doc <- gsub("txt", "", doc)
  return(doc)
}


# function to remove special characters
lyrics$Content <- sapply(lyrics$Content, fix.contractions)
lyrics$FileName <- sapply(lyrics$FileName, fix.contractions)



# remove special characters


removeSpecialChars <- function(x) gsub("[^a-zA-Z0-9 ]", " ", x)

lyrics$Content <- sapply(lyrics$Content, removeSpecialChars)
lyrics$FileName <- sapply(lyrics$FileName, removeSpecialChars)


# convert everything to lower case
lyrics$Content <- sapply(lyrics$Content, tolower)
lyrics$Filename <- sapply(lyrics$FileName, tolower)

content <- lyrics$Content
name <- lyrics$FileName

lyrics_df <- tibble(name = 1:49, text = content)
lyrics2_df <- lyrics_df %>%
  unnest_tokens(word, text)

data(stop_words)

lyrics2_df <- lyrics2_df %>%
  anti_join(stop_words)

lyrics2_df %>%
  count(word, sort = TRUE)

lyrics2_df
```

```{r}
lyrics2_df %>%
  count(word, sort = TRUE) %>%
  filter(n > 30) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```


# Works Cited
