---
title: "Average Sentiment on a Song by Song Basis"
date: 2020-03-13T14:19:53-05:00
draft: false
links:
  - icon_pack: fab
    name: Docs
    url: courses/example1
  - icon_pack: fab
    name: Slides
    url: slides/example
  - icon_pack: fab
    name: Project
    url: project1/internal-project
bibliography: /home/redapemusic35/VimWiki/Exported-Items.bib
---

Here are some of my initial attempts at performing sentiment analyses on my data sets. 

Below, what you'll see are two sets of graphs. The first shows the sentiment on a per song basis of all of the files that I have categorized as country music. The first song, at the top of the graph "I Hope You're Happy Now," is the most positive whereas the song "More Hearts Than Mine," is the least.

Here, the sentiment probability ranges from -1 being the most negative to 1 being the most positive with 0 being neutral.

```{r echo = FALSE, results='hide',message=FALSE}
library(dplyr)
library(tidytext)
library(tidyverse)
library(graphics)
library(ggplot2)
setwd("~/mallet")
hext <- read.csv("Country_keys.csv")
hext4 <- read.csv("Country_word_topics.csv")
```

```{r echo = FALSE, message = FALSE}
library(sentimentr)
require(data.table)
library(vroom)
library(readr)
library(dplyr)
library(tidytext)
library(tidyverse)
library(graphics)
library(ggplot2)
setwd("~/mallet")
hext <- read.csv("Country_keys.csv")
hext4 <- read.csv("Country_word_topics.csv")
list_of_files <- list.files(path = "sample-data/top100/Country/", recursive = TRUE,
			    pattern = "\\.csv$",
			    full.names = TRUE)
df <- list_of_files %>%
  purrr::set_names(nm = (basename(.) %>% tools::file_path_sans_ext())) %>%
  purrr::map_df(read_csv,
		col_names = FALSE,
		skip = 1,
		.id = "FileName")

(dfsentiment <- with(
		     df,
		     sentiment_by(
				  get_sentences(X1),
				  list(FileName)
				  )
		     ))


plot(dfsentiment)

```

First up, you'll notice that the song "I Hope You're Happy Now" expresses the most positive emotions with an average overall sentiment of 0.20356317 and "Breaking More Hearts than Mine" expressing the most negative at -0.17603473. Each of the grey transparent points in the graph represent the individual sentences in the lyric sets. On the next page, we will do some closer analysis on each sentence.

```{r echo = FALSE, results='hide',message=FALSE}
library(magrittr)
library(sentimentr)
require(data.table)
library(vroom)
library(readr)
library(dplyr)
library(tidytext)
library(tidyverse)
library(graphics)
library(ggplot2)
setwd("~/mallet/")
list_of_files2 <- list.files(path = "sample-data/top100/Rap/", recursive = TRUE,
			    pattern = "\\.csv$",
			    full.names = TRUE)

df2 <- list_of_files2 %>%
  purrr::set_names(nm = (basename(.) %>% tools::file_path_sans_ext())) %>%
  purrr::map_df(read_csv,
		col_names = FALSE,
		skip = 1,
		.id = "FileName2")



(dfsentiment2 <- with(
		     df2,
		     sentiment_by(
				  get_sentences(X1),
				  list(FileName2)
				  )
		     ))

df3 <- df2 %>%
  dplyr::mutate(X1_split = get_sentences(X1)) %$%
  sentiment_by(X1_split, list(FileName2))


```

Next, we do the same to the group of songs that I have categorized as Hip-Hop.

```{r echo = FALSE, message = FALSE}


df3
plot(df3)
```
Previously, we looked at individual terms which made up the topics of the songs comprising our data sets. These "topics," more often than not are terms which we might say that that song is about. While doing so was certainly illuminating, it was difficult to see what about these terms constituted moral knowledge. For instance, if one topic was comprised of terms like murder, death, anger and whatnot, this does not necessarily mean that the song says that these things are good, or admirable, or desirable character traits. 

[Moral Cognitivism and Moral Non-cognitivism](https://plato.stanford.edu/entries/moral-cognitivism/) are ethical views more commonly associated with metaethics than they are with standard ethical theories. Moral non-cognitivists will often say that there is no such thing as moral facts, meaning that phrases like "that was a good action," or "John is a good person," means nothing more than "that action made me *feel* good" or "John is a person who gives me pleasant feelings." 

> Non-cognitivists agree ... that there are no moral properties or moral facts... Roughly put, non-cognitivists think that moral statements have no substantial truth conditions...[people when expressing moral beliefs] are expressing non-cognitive attitudes more similar to desires, approval or disapproval. [@van18]

It is plausible, one could argue, that another reason that looking at topics would not tell us whether a song lyric contains moral knowledge or not, is because there are no moral facts. So, a set of song lyrics which consist of topics like murder and so on are not really expressing immoral facts, for instance, but maybe they are just expressions of what someone finds admirable or attractive.

> if judging that eating meat is wrong is really a matter of expressing one's own emotional disapproval towards eating meat, then so long as I currently feel no disapproval towards meat eating, the mere fact that someone else judges that meat eating is wrong seems to be neither here nor there. [@mcgr19, 79]

As such, on the one hand, we might push back against the individual who says that song lyrics cannot corrupt morally, meaning that they cannot undermine someone's moral knowledge, because there were never any moral facts to be known in the first place. As such, it is impossible to have moral knowledge and therefore impossible to undermine it.

Part of what I suggest in the following sections, is that this is a dangerous idea. Whether or not someone believes that there are moral facts or there are not, this says nothing about whether it is possible to affect the way we feel about situations / scenarios and actions. For instance, I may say that hording n95 masks is reprehensible. Another may respond by saying that I am merely expressing my opinion which itself is formed by the emotions that are invoked in me when I hear or experience someone hording. However, we do not know specifically why I might feel the way I do about hording. According to McGrath, our moral views are inherited from our social environment [@mcgr19, 8]. As such, I may think that hording is wrong because I inherited this view from my social environment. As such, the reason that I feel the way I do about hording, is because of this social environment.

In the next few sections, I will be looking at different methods to determine the emotional content of the song lyrics which we have been looking at this far for some excellent methods and tutorials used to put this together.[^5] What I think emerges when we do this, is that some songs attribute positive emotional sentiments to subjects which  seem likely that everyone might agree are fairly reprehensible. However, a part of what I find important about sentiment analysis, are those associations between expressed sentiments in songs, and the topics which these sentiments are associated with. Whether or not we adopt the sentiments we do because of associations like these remains to be seen. So if a song is about murder for instance, and the sentiments expressed in such a song are purely positive, then does this mean that a social environment which consists of such a song, is one wherein the associations between murder and emotions are positive ones? Would someone coming from such an environment be more dispositioned to feel positive emotions, and thereby approve of murder?

[^5]: see @rink20 and @jock17

## Sources

For my sources, I refer to those files that I have used throughout the project. These include individual text files, .txt, composed of song lyrics which I copied from either google searches or the billboard top100 list on March 13. The csv files shown were used in other aspects of the project but consist of the same lyric data as the txt files. I merely keep them in the same folders as the txt files because it makes it easier to manipulate the data. Essentially, I can point R to one folder and perform many different kinds of code on the files in that folder. 

```{r echo = FALSE, message = FALSE}
library(dplyr)
library(tidytext)
library(tidyverse)
library(graphics)
library(ggplot2)
setwd("~/mallet/")
hext <- read.csv("Country_keys.csv")
hext4 <- read.csv("Country_word_topics.csv")
hext5 <- list.files(path = "~/mallet/sample-data/top100/Country")
hext6 <- list.files(path = "~/mallet/sample-data/top100/Rap")
```

### "Country" Songs

```{r echo = FALSE, message = FALSE}


hext5
```

### "Hip Hop" Songs

Here, you will probably notice that there are some files labled "filelist2" etc. These were used to populate some list in another aspect of the project. However, I do not want to delete them because I forget exactly where or how they were used.

```{r echo = FALSE, message = FALSE}


hext6

```

In the next few frames, I am merely showing some of the contents of the files themselves. For instance, the frame immediately following shows the filenames of "Catch" as well as the kind of data that is used for the analysis, which is a "tibble." I expect to have a better understanding (hopefully), of some of the more theoretical aspects behind the process as my time spent on this project progresses. The two frames following the immediate one merely consist in the first and last six lines of data processed through this particular bit of code (remember that I plan on having an area which provides instructions on how to recreate my analysis yourself).

```{r echo = FALSE, message = FALSE}
library(sentimentr)
require(data.table)
library(vroom)
library(readr)
library(dplyr)
library(tidytext)
library(tidyverse)
library(graphics)
library(ggplot2)
setwd("~/mallet/")
hext <- read.csv("Country_keys.csv")
hext4 <- read.csv("Country_word_topics.csv")
list_of_files <- list.files(path = "sample-data/top100/Country/", recursive = TRUE,
			    pattern = "\\.csv$",
			    full.names = TRUE)
df <- list_of_files %>%
  purrr::set_names(nm = (basename(.) %>% tools::file_path_sans_ext())) %>%
  purrr::map_df(read_csv,
		col_names = FALSE,
		skip = 1,
		.id = "FileName")


str(df)
head(df)
tail(df)
```
Finally, some fun preliminary observations. For instance, the frame immediately following organizes the data according to song shown in the second column and titled "Filename" following the numbered order of the song. The column after "Filename" which is labeled "word_count" shows the number of words in that song. The final column "ave_sentiment" shows the average sentiment expressed in that song lyric. Average sentiment is represented by a 9 place decimal number between -1 and 1 with -1 being negative emotion and 1 the opposite. 0 is neutral.

```{r echo = FALSE, message = FALSE}


(dfsentiment <- with(
		     df,
		     sentiment_by(
				  get_sentences(X1),
				  list(FileName)
				  )
		     ))

```

The frame following shows a pretty graph of the above data and ranked according to expressed sentiment most negative at the bottom of the graph and most positive at the top. I should point out here, that the smallish grey dots ranging in opacity represent individual sentences ordered graphically according to the range of negative or positive sentiment expressed in that particular sentence. As such, the red diamond represents the average expressed sentiment of all of the sentences. Where the dots are considerably darker, represent multiple sentences expressing the same sentiment. Because these converge in terms of the sentiment expressed, they overlap on the graph and this is shown by a gradual darkening of the point.


```{r echo = FALSE, message = FALSE}


plot(dfsentiment)
```

```{r echo = FALSE, message = FALSE}
library(magrittr)
library(sentimentr)
require(data.table)
library(vroom)
library(readr)
library(dplyr)
library(tidytext)
library(tidyverse)
library(graphics)
library(ggplot2)
setwd("~/mallet/")
list_of_files2 <- list.files(path = "sample-data/top100/Rap/", recursive = TRUE,
			    pattern = "\\.csv$",
			    full.names = TRUE)
df2 <- list_of_files2 %>%
  purrr::set_names(nm = (basename(.) %>% tools::file_path_sans_ext())) %>%
  purrr::map_df(read_csv,
		col_names = FALSE,
		skip = 1,
		.id = "FileName2")
```

### "Hip Hop" Songs

First, like we did with the country songs, the below frames show various attributes of our data. Remember that these are not complete as they merely give us a brief look at the data. What we see is that the data is defined in terms of each file. Therefore, the first six lines of the data file consists in the first six lines of the song "Ballin" since "Ballin" is the file which the program read first. The next frame consists of the last six lines of our data frame which equals that last six lines of the song "Woah" since "Woah" is the last file read by R.

```{r echo = FALSE, message = FALSE}


str(df2)
```

```{r echo = FALSE, message = FALSE}


head(df2)
tail(df2)
```

As before, the next frame show each file in the data set. Next to those are 3 columns of data. The first column is the word count of each file, the last column is the average sentiment by file.

```{r echo = FALSE, message = FALSE}


(dfsentiment2 <- with(
		     df2,
		     sentiment_by(
				  get_sentences(X1),
				  list(FileName2)
				  )
		     ))
```

The above but in a nice graph. You might notice that some of the sentiments expressed here go beyond -1. I find this interesting because as you might remember when we did the topic modeling, the topics expressed by the hip-hop lyrics were drastically more widespread and varied. This seems to also be the case concerning the expressed sentiments, namely that the emotions expressed are more widespread and varied than those expressed in the country songs. I do not think that this finding means anything, it might just be because the hip-hop songs use more words in general and so the program interprets this as more meanings. But in truth, I have not thought much about this.

```{r echo = FALSE, message = FALSE}


plot(dfsentiment2)
```

Here is another fun, preliminary aspect of the method. What the below frames shows, are the various emotions expressed by the documents. To the left, you will find the song titles while the top of each chart shows the expressed emotion. Once again, the grey points, or dots represent the individual sentences in that document which account for the attributed emotional score.

A couple of points that I find interesting initially, but I have not yet thought about this too much, is that the chart titled "anger," "disgust," "sadness," and "fear," shows a clustering of sentences (complete with fairly far reaching outliers) that is more loose than that shown by the more positive emotions of "joy," "trust," and "anticipation." For instance, one of the sentences expresses "fear" at 100%! And the same goes for sadness!! And disgust!!! And anger!!!!

```{r echo = FALSE, message = FALSE}


df3 <- df2 %>%
  dplyr::mutate(X1_split = get_sentences(X1)) %$%
  emotion_by(X1_split, list(FileName2))

df4 <- df2 %>%
  dplyr::mutate(X1_split = get_sentences(X1)) %$%
  sentiment_by(X1_split, list(FileName2))

plot(df3)
plot(df4)
```

I wonder what a similar chart will show of the country set...

```{r echo = FALSE, message = FALSE}
df7 <- df %>%
  dplyr::mutate(X1_split = get_sentences(X1)) %$%
  emotion_by(X1_split, list(FileName))

df8 <- df %>%
  dplyr::mutate(X1_split = get_sentences(X1)) %$%
  sentiment_by(X1_split, list(FileName))

plot(df7)
plot(df8)

```

Initially, it seems as though the opposite holds true. The clustering of sentences expressing "joy," "anticipation," "trust," is more loose whereas those expressing "anger" etc shows a tighter clustering.

The last thing that I will do on this page is show the profanity rating of each song just because I can.

First up, hip-hop songs... 

Look at the song titled "Life is Good." Apparently there is a sentence therein which expresses what I take to be the phrase; "Life is good (expletive)." Cheery.

```{r echo = FALSE, message = FALSE}

df6 <- df2 %>%
  dplyr::mutate(X1_split = get_sentences(X1)) %$%
  profanity_by(X1_split, list(FileName2))

plot(df6)

```

Next, country...

```{r echo = FALSE, message = FALSE}

df9 <- df %>%
  dplyr::mutate(X1_split = get_sentences(X1)) %$%
  profanity_by(X1_split, list(FileName))

plot(df9)

```

As you might have expected as I have, nothing.

This is one of the more taxing portions of the project. However, I believe that it is the most illuminating in a project of this type. First, one of the concerns I had with attempting to find moral knowledge among song lyrics, I was worried that the temptation would be to count the overall negative and positive words among a song's lyrics.

For instance, among some of my earlier attempts, I noticed that a song's lyrics might include many terms which I thought were quite negative, such as song's about murder and prison sentences. However, Stanford's Core NLP sometimes attributed positive scores to these examples. I was perplexed, thinking that either I ran the program wrong, or that the program was exhibiting a potential fault. I don't think that this is the case anymore, but rather that I was looking at the lyrics and understanding the content in terms of weights of various terms, rather than attempting to understand their context.

This I think leads us to one of the primary benefits that sentiment analysis affords us. Essentially, sentiment analysis understands how terms are used in the context of the data set. 

I am not sure how exactly, but here is a link that examples some of the differences among [sentiment analysis methods](https://nlp.stanford.edu/pubs/StanfordCoreNlp2014.pdf).



In this portion, I will only focus on three sets of examples, "The Bones" by Maren Morris, "Homesick" by Kane Brown, and a random example passage for comparison's sake.


First, the lyrics to "The Bones."

```{r echo = FALSE}
library(syuzhet)
library(tokenizers)

Bones1_v <- get_text_as_string(path = "/home/redapemusic35/mallet/sample-data/top100/Country/bones.txt")
homesick1_v <- get_text_as_string(path = "/home/redapemusic35/mallet/sample-data/top100/Country/homesick.txt")

Bones2_v <- tokenize_sentences(Bones1_v, lowercase = FALSE, strip_punct = FALSE, simplify = FALSE)
homesick2_v <- tokenize_sentences(homesick1_v, lowercase = FALSE, strip_punct = FALSE, simplify = FALSE)

Bones2_v

my_example_text <- "I begin this story with a neutral statement.  
  Basically this is a very silly test.  
  You are testing the Syuzhet package using short, inane sentences.  
  I am actually very happy today. 
  I have finally finished writing this package.  
  Tomorrow I will be very sad. 
  I won't have anything left to do. 
  I might get angry and decide to do something horrible.  
  I might destroy the entire package and start from scratch.  
  Then again, I might find it satisfying to have completed my first R package. 
  Honestly this use of the Fourier transformation is really quite elegant.  
  You might even say it's beautiful!"
s_v <- get_sentences(my_example_text)

Ballin_v <- get_text_as_string(path = "/home/redapemusic35/mallet/sample-data/top100/Rap/Ballin.txt")
Life_v <- get_text_as_string(path = "/home/redapemusic35/mallet/sample-data/top100/Rap/Life-is-good.txt")

Ballin_v1 <- tokenize_sentences(Ballin_v, lowercase = FALSE, strip_punct = FALSE, simplify = FALSE)
Life_v1 <- tokenize_sentences(Life_v, lowercase = FALSE, strip_punct = FALSE, simplify = FALSE)

Life_v1
Ballin_v1
```

Next, the lyrics to "Homesick." In this set, I had to fix a lot of contractions, words like "I'm" and "ain't" and "we'll." You might notice that some of the lyrics seem a bit off, this is why.

```{r echo = FALSE}

fix.contractions <- function(doc) {
  doc <- gsub("won't", "will not", doc)
  doc <- gsub("can't", "can not", doc)
  doc <- gsub("n't", " not", doc)
  doc <- gsub("'re", " are", doc)
  doc <- gsub("'ve", " have", doc)
  doc <- gsub("'m", " am", doc)
  doc <- gsub("'d", " would", doc)
  doc <- gsub("flyin'", "flying", doc)
  doc <- gsub("'s", "", doc)
  doc <- gsub("Puttin'", "Putting", doc)
  doc <- gsub("I'll", "I will", doc)
  doc <- gsub("payin'", "paying", doc)
  doc <- gsub("we'll", "we will", doc)
  doc <- gsub("We'll", "We will", doc)
  doc <- gsub("singin'", "singing", doc)
  doc <- gsub("you'll", "you will", doc)
  doc <- gsub("'em", "them", doc)
  doc <- gsub("dancin'", "dancing", doc)
  doc <- gsub("playin'", "playing", doc)
  doc <- gsub("ain't", "have not", doc)
  doc <- gsub("Ain't", "Have not", doc)
  doc <- gsub("They'll", "They will", doc)
  doc <- gsub("they'll", "they will", doc)
  doc <- gsub("gettin'", "getting", doc)
  doc <- gsub("ain't", "am not", doc)
  doc <- gsub("Gettin'", "getting", doc)
  doc <- gsub("'cause", "be cause", doc)
  doc <- gsub("ain", "is not", doc)
  doc <- gsub("'bout", "about", doc)
  return(doc)
}


homesick2_cont <- sapply(homesick2_v, fix.contractions)
Ballin_cont <- sapply(Ballin_v1, fix.contractions)
Life_cont <- sapply(Life_v1, fix.contractions)

Life_cont
Ballin_cont
homesick2_cont
```

Finally, my example text. Disclosure, the code used on this page, as well as the example below I adopted from Matthew @jock17's excellent introduction to the [Syuzhet package for R](https://cran.r-project.org/web/packages/syuzhet/vignettes/syuzhet-vignette.html).

```{r echo = FALSE}

s_v

```

I next get the song sentiments and do provide some lists which show the sentences which are joyful and those expressing anger. What is great about "nrc" is that I could display those sentences expressing anger, anticipation, disgust, fear, joy, sadness, surprise, and trust.

```{r echo = FALSE}


Bones3_v <- get_sentences(Bones1_v)
homesick3_v <- get_sentences(homesick2_cont)

nrc_data <- get_nrc_sentiment(Bones3_v)
nrc_data1 <- get_nrc_sentiment(homesick3_v)

Ballin_v2 <- get_sentences(Ballin_cont)
Life_v1 <- get_sentences(Life_cont)

nrc_dataB <- get_nrc_sentiment(Ballin_v2)
nrc_dataL <- get_nrc_sentiment(Life_v1)

```

Sentences expressing anger in "The Bones," "Homesick," "Ballin," and "Life is Good."

```{r echo = FALSE}
angry_items <- which(nrc_data$anger > 0)
Bones3_v[angry_items]
angry_items1 <- which(nrc_data1$anger > 0)
homesick3_v[angry_items1]

angry_itemsB <- which(nrc_dataB$anger > 0)
Ballin_v2[angry_items]
angry_itemsL <- which(nrc_dataL$anger > 0)
Life_v1[angry_itemsL]
```

Look at the relationship terms used in these two categories of lyrics. In the first song, "The Bones," it seems that the anger is expressed towards outside forces, namely that it is not directed at another person. The second song, it is less clear what the anger is being expressed towards. In "Ballin," it is not necessarily clear why the anger is there. Looking at these sentences alone, it appears that the author is merely stating that he's achieved wealth and success, yet, there is underlying anger still for whatever reason. It just isn't clear in this context. Finally, "Life is Good," is expressing anger at others, so here there are relationship terms being used, however they are being used in a negative fashion.

Sentences expressing joy in "The Bones."

```{r echo = FALSE}
joy_items <- which(nrc_data$joy > 0)
Bones3_v[joy_items]
```

In "Ballin," the joy appears directed at objects whereas in "The Bones," joy is being expressed at accomplishment. Further, the relationship terms here are being used to express that the achievement was accomplished by way of the relationship itself. This seems to also be the case in the song "Homesick."

```{r echo = FALSE}
joy_itemsB <- which(nrc_dataB$joy > 0)
Ballin_v2[joy_itemsB]
```
Joy in "Homesick."

```{r echo = FALSE}


joy_items1 <- which(nrc_data1$joy > 0)
homesick3_v[joy_items1]
```

In life is good, it appears that some of the same sentences expressing joy were also those that expressed anger. Therefore it is not clear whether the joy is directed at the relationship with 2nd person object in these sentences, or the non-personal objects such as his wrist watch.

```{r echo = FALSE}


joy_itemsL <- which(nrc_dataL$joy > 0)
Life_v1[joy_itemsL]
```
Anticipation in "The Bones."

```{r echo = FALSE}
anticipation_items <- which(nrc_data$anticipation > 0)
Bones3_v[anticipation_items]

```

Regarding "The Bones," I am having difficulty seeing what is attributed as anticipation is such. For instance consider line 3; "Call it dumb luck, but baby, you and I cannot even mess it up, although we both try." The anticipation expressed here, seems to me subtle if I am being generous.

Anticipation in "Homesick."

```{r echo = FALSE, message = FALSE}



anticipation_items1 <- which(nrc_data1$anticipation > 0)
homesick3_v[anticipation_items1]
```

Here is a table of all the expressed sentiments and their relative weights in the song "The Bones."

```{r echo = FALSE, message = FALSE}
pander::pandoc.table(nrc_data[, 1:8], split.table = Inf)

valence <- (nrc_data[, 9]*-1) + nrc_data[, 10]
```

Here is a table of all the expressed sentiments and their relative weights in the song "Homesick."

```{r echo = FALSE, message = FALSE}


pander::pandoc.table(nrc_data1[, 1:8], split.table = Inf)

valence1 <- (nrc_data1[, 9]*-1) + nrc_data1[, 10]
```

Better displays of the above information. This graph shows the percentages of the shown emotions. For instance, joy is the most expressed emotion in the song "The Bones" at about 24%.

```{r echo = FALSE, message = FALSE}
barplot(
	sort(colSums(prop.table(nrc_data[, 1:8]))),
	horiz = TRUE,
	cex.names = 0.7,
	las = 1,
	main = "Emotions in The Bones", xlab = "Percentage"
	)
```
```{r echo = FALSE}


barplot(
	sort(colSums(prop.table(nrc_data1[, 1:8]))),
	horiz = TRUE,
	cex.names = 0.7,
	las = 1,
	main = "Emotions in Homesick", xlab = "Percentage"
	)
```

The graph below is an emotional valence chart. What it shows are the emotions expressed as the lyrics progress throughout the song. Further, the graph compares the emotional valence, of the expressions of sentiment in each song as they progress. The red line represents the emotional valence in "The Bones," while the blue line represents the emotional valence in "Homesick."

```{r echo = FALSE, message = FALSE}




Bones_sent <- get_sentiment(Bones3_v, method="syuzhet")
homesick_sent <- get_sentiment(homesick3_v, method="syuzhet")
s_v1 <- get_sentiment(s_v, method="syuzhet")

pwdw <- round(length(Bones_sent)*.1)
poa_rolled <- zoo::rollmean(Bones_sent, k=pwdw)
bwdw <- round(length(homesick_sent)*.1)
bov_rolled <- zoo::rollmean(homesick_sent, k=pwdw)
cwdw <- round(length(s_v1)*.1)
cov_rolled <- zoo::rollmean(s_v1, k=cwdw)

poa_list <- rescale_x_2(poa_rolled)
bov_list <- rescale_x_2(bov_rolled)
cov_list <- rescale_x_2(cov_rolled)

str(poa_list)
class(poa_list)

plot(poa_list$x,
     poa_list$z,
     type="l",
     col="blue",
     xlab="Narrative Time",
     ylab="Emotional Valence")
lines(bov_list$x, bov_list$z, col="red")
lines(cov_list$x, cov_list$z, col="black", lwd=3)

poa_sample <- seq(1, length(poa_list$x), by=round(length(poa_list$x)/50))
bov_sample <- seq(1, length(bov_list$x), by=round(length(bov_list$x)/50))
```

Here, I introduce similar analyses on lyrics in the Hip Hop category. What might be possible here, is to determine sentiment is applied on similar topics our not. My initial thought is that it will not be. Given that there were a larger percentage of relationship terms in the country category than the Hip Hop category, it will be interesting to see whether those sentences expressing joy in the Hip Hop category involve topics which have to do with objects, for instance cars, money etc, then it would be directed at relationships. For instance, those sentences expressing joy in "Homesick," were directed at others. I look forward to seeing what sentences expressing joy in Hip Hop songs are directed towards. This is very similar to the section wherein I showed some specific sentences which expressed anger, or joy. 

In the following frame, I show a bar graph showing those percentages which each emotion is expressed in first the song "Ballin'" and then "Life is Good."

```{r echo = FALSE, message = FALSE}
barplot(
	sort(colSums(prop.table(nrc_dataB[, 1:8]))),
	horiz = TRUE,
	cex.names = 0.7,
	las = 1,
	main = "Emotions in Ballin'", xlab = "Percentage"
	)
```
```{r echo = FALSE}


barplot(
	sort(colSums(prop.table(nrc_dataL[, 1:8]))),
	horiz = TRUE,
	cex.names = 0.7,
	las = 1,
	main = "Emotions in Life is Good", xlab = "Percentage"
	)
```

I then do the same with the songs "The Bones," and "Homesick."

```{r echo = FALSE}
barplot(
	sort(colSums(prop.table(nrc_data[, 1:8]))),
	horiz = TRUE,
	cex.names = 0.7,
	las = 1,
	main = "Emotions in The Bones", xlab = "Percentage"
	)
```
```{r echo = FALSE}


barplot(
	sort(colSums(prop.table(nrc_data1[, 1:8]))),
	horiz = TRUE,
	cex.names = 0.7,
	las = 1,
	main = "Emotions in Homesick", xlab = "Percentage"
	)
```

It is telling to me, that those emotions which hold the highest percentages in these four songs, are opposite one another. For instance, fear and sadness are at the top of Ballin' while anger and fear is at the top of "Life is Good." However, in the songs "Homesick," and "The Bones," you have sadness (Homesick, which we would expect), and joy, while in "The Bones," we have joy and surprise being expressed the most.

Finally, because fear has a really high percentage in both "Ballin" and "Life is Good," I wanted to see which sentences contributed towards this.

```{r echo = FALSE, message = FALSE}
fear_itemsB <- which(nrc_dataB$fear > 0)
Ballin_v2[fear_itemsB]
fear_itemsL <- which(nrc_dataL$fear > 0)
Life_v1[fear_itemsL]
```

The results here are not clear to me. I cannot tell what it is about these sentences that expresses fear. Maybe someone can help me out here.

# Works Cited
